Need a good title. Submit to Methods of Ecology and Evolution or Evolutionary Biology

### 2018-04-04 main.tex
temp pushing first 2 paragraphs

Phylogenetic comparative methods have been widely used to study species relativeness problems.
Phylogenetic models aim to find parsimonious methods that can be used to link ecological phenomena with evolutionary processes by incorporating the historical relationships shared across species via phylogenetic (evolutionary) trees. 
\ml{parsimonious can be a confusing word here}
Although such models attempt to account for species correlations, they often make strong and over-simplified assumptions of the evolutionary process. 
Decades of work have created various different methods that enables researchers to incorporate phylogenetic effects in analyzing species relativeness applications.
But many challenges remain.
In particular, accounting for phylogenetic effects in high dimensional systems is always challenging, especially for models incorporating multiple forms of phylogenetic effects, and especially with large phylogenies where computation powers are limited.
\ml{Define phylogenetic effects. PE can mean a lot of different things (see Pagel's tree transformation). What we mean here is strictly phylogenetic signal-- extent to which trait/response values are statistically related to phylogeny.}
Ignoring phylogenetic effects/signals can be problematic both biologically and statistically \citep{felsenstein1985phylogenies, li2017statistical} -- in such cases, researchers often use simpler models accounting for minimal phylogenetic signals by limiting at the individuals level and neglect additional phylogenetic signals present in the system.

@@

The typical phylogenetic regression is of the form:
\begin{align}
y & = XB + \epsilon \\
\epsilon & \sim MVN(0,\sigma^{2}C),
\label{eq:gls}
\end{align}
where $y$ is an $n \times 1$ vector of measurable response; $X$ is an $n \times (m + 1)$ model matrix containing 1's in the first column and the $m$ independent variable (phenotypic traits or environmental variable); $B$ is an $m + 1$ coefficient vector; $\epsilon$ is the residual error and assumed to be multivariate normally distributed with a variance-covariance matrix given by $\sigma^{2}_{\epsilon}C$ in which $C$ is an $n \times n$ matrix of the phylogenetic correlation (PC).

>>>>

Phylogenetic comparative methods (PCM) aim to find parsimonious models that link traits and ecological phenomena with evolutionary processes by incorporating the historical relationships shared among taxa as represented by phylogenetic (evolutionary) trees.
The primary approach to incorporate this link is by transforming the phylogenetic relationship in the evolutionary tree into species phylogenetic correlation matrices.
Phylogenetic generalized least square regression (PGLS) and phylogenetic generalized linear mixed models (PGLMM) are classic methods that uses this approach; they have been widely and effectively used.
However, despite the widespread use of these classic PCMs, many analytic tools available are inflexible and computationally inefficient.
As a result, researchers have often overlooked and avoided using PCMs. 
In this paper, we proposed an more flexible and computationally efficient alternative method that incorporates phylogenetic correlations as a Gaussian process, modeling the evolutionary changes along each branch of a phylogenetic tree as independent (possibly multivariate) random Normal deviates.

Ever-increasing capabilities of genetic sequencing techniques are making genomic data available over an ever-wider range of species and also higher resolutions in their evolutionary relationships.
As a result, researchers are interested in exploring more complicated systems and fitting more complicated models to their data. 
Given a phylogenetic tree, it is relatively simple to compute a corresponding correlation matrix, which can be incorporated in statistical methods.
The most widely used statistical process in phylogenetic comparative analysis to model evolutionary process is the pure random drift process, Brownian motion \citep{felsenstein1973maximum}. 
Although the Brownian motion is an over-simplified model of evolution, many of the existing phylogenetic comparative methods are built upon.
For example, phylogenetically independent contrasts (PICs) \citep{felsenstein1985phylogenies}, phylogenetic generalized least squares (PGLS) \citep{grafen1989phylogenetic}, Pagel's $\lambda$ \citep{pagel1999inferring}, and Blomberg's $K$ \citep{blomberg2003testing} are methods developed in the last couple of decades and have provided important insights in this field. 
But for technical reasons, all of these approaches are slow (computationally inefficient) or inflexible in terms of degrees of phylogenetic variabilitity.

______

Phylogenetic comparative methods (PCM) aim to find parsimonious models that link traits and ecological phenomena with evolutionary processes by incorporating the historical relationships shared among taxa as represented by phylogenetic (evolutionary) trees. 
Decades of work have created various different methods that enables researchers to incorporate phylogenetic effects in analyzing species relativeness applications, yet existing methods are still have strong contraints. 
In particular, the current stat
% But many challenges remain.
In particular, accounting for phylogenetic effects in high dimensional systems is always challenging, especially for models incorporating multiple forms of phylogenetic effects, and especially with large phylogenies where computation powers are limited.
% \ml{Define phylogenetic effects. PE can mean a lot of different things (see Pagel's tree transformation). What we mean here is strictly phylogenetic signal-- extent to which trait/response values are statistically related to phylogeny.}
Ignoring phylogenetic effects/signals can be problematic both biologically and statistically \citep{felsenstein1985phylogenies, li2017statistical} -- in such cases, researchers often use simpler models accounting for minimal phylogenetic signals by limiting at the individuals level and neglect additional phylogenetic signals present in the system.

@@

The typical phylogenetic regression is of the form:
\begin{align}
y & = XB + \epsilon \\
\epsilon & \sim \textrm{MVN}(0,\sigma^{2}C),
\label{eq:gls}
\end{align}
where $y$ is an $n \times 1$ vector of measurable response; $X$ is an $n \times (m + 1)$ model matrix containing 1's in the first column and the $m$ independent variable (phenotypic traits or environmental variable); $B$ is an $m + 1$ coefficient vector; $\epsilon$ is the residual error and assumed to be multivariate normally distributed with a variance-covariance matrix given by $\sigma^{2}_{\epsilon}C$ in which $C$ is an $n \times n$ matrix of the phylogenetic correlation (PC).
